Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-19 README.Rmd
add altmetric

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

>>>>

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>

<table>
<tbody>
  <tr>
    <td><div data-badge-popover="right" data-badge-type="1" data-doi="10.31234/osf.io/fwxs4" data-hide-no-mentions="true" class="altmetric-embed"></div></td>
    <td>Preregistration as Code: <a href="https://doi.org/10.5281/zenodo.5170740" target="_blank" rel="noopener noreferrer">[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5170740.svg)](https://doi.org/10.5281/zenodo.5170740)</a></td>
  </tr>
  <tr>
    <td><a href="https://www.repostatus.org/#active" target="_blank" rel="noopener noreferrer">[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)</a></td>
    <td>Results after Preregistration: <a href="https://doi.org/10.5281/zenodo.5171678">[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5171678.svg)](https://doi.org/10.5281/zenodo.5171678)</a></td>
  </tr>
</tbody>
</table>

<!-- badges: end -->
